Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-10 minimax.tex
Rm some TODOs done.
Page numbers
Wording intro

\pagestyle{fancy}
\fancyhead{}

@@

The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective.
\Cref{sec:background} provides the necessary background and \cref{sec:mmr} introduces the minimax criterion, a method that selects a winner that minimizes the worst possible regret.
In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  Section \ref{sec:experiments} presents the experiments validation of our approach and the guidelines stemming from these simulations; and Section \ref{sec:conclusions} provides some final thoughts.

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
%TODO
%\begin{enumerate}
%	\item Reach regret: $n/10$. Add considerations.
%Graphs: Reduce number of marks on the X axis.
%MMR and sd with systematically one decimal exactly
%Pessimistic systematically better than XPess?
%Page numbers
%reflexive?
%\end{enumerate}
We  performed a number of numerical experiments in order to validate our approach and to test the performance of the different elicitation strategies. %Our experiments are described by topic here below. 
We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, containing the true preferences of the agents (i.e. the linear orders) and the weights associated with the chair's scoring rule. 
The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing. 
For generating the weights we first draw $m - 1$ numbers uniformly at random (representing weight ``differences''), normalize and sort them; 
a sequence of convex decreasing weight is then obtained by a decumulative sum.
The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.

>>>>

\pagestyle{fancy}
\fancyhead{}
\setlength{\footskip}{1.6cm}
\cfoot{\thepage}

@@

The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective.
\Cref{sec:background} provides the necessary background and \cref{sec:mmr} introduces the minimax criterion, a method that selects a winner that minimizes the worst possible regret.
In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  Section \ref{sec:experiments} presents an experimental validation of our approach and some guidelines stemming from these simulations; and Section \ref{sec:conclusions} provides some final thoughts.

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
%TODO
%\begin{enumerate}
%	\item Reach regret: $n/10$. Add considerations.
%MMR and sd with systematically one decimal exactly
%Page numbers
%\end{enumerate}
We  performed a number of numerical experiments in order to validate our approach and to test the performance of the different elicitation strategies. %Our experiments are described by topic here below. 
We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, containing the true preferences of the agents (i.e. the linear orders) and the weights associated with the chair's scoring rule. 
The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing. 
For generating the weights we first draw $m - 1$ numbers uniformly at random (representing weight ``differences''), normalize and sort them; 
a sequence of convex decreasing weight is then obtained by a decumulative sum.
The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
